### 2024-03-16 content/chapter_1.tex
:lipstick: Add reflected wave plots

\begin{section}{Background and Motivation}
	The quest for better wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
	Great successes have been made at the transmitter and receiver sides over the past century, and the communications society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
	By 2025, global mobile data traffic is expected to reach {607} exabytes per year \cite{Tariq2020} while the number of connected devices may exceed {75} billion \cite{Georgiev2024}.
	At the same time, wireless applications are also evolving in various forms to address world-changing incidents like COVID-19, climate change, geopolitical tensions, and \gls{ai} revolution.
	An initial attempt was made in 5G where the network prioritizes among high-throughput, ubiquitous-coverage, high-reliability, low-latency, massive-connectivity, and energy-efficient services \cite{Shafi2017}.
	However, the desire of human and machine for better communication shows no signs of slowing down.
	Emerging applications such as smart cities, autonomous driving, telemedicine, extended reality, federated learning, and generative intelligence are calling for a stronger and smarter wireless infrastructure.
	It is envisioned that 6G will be designed to meet the following requirements \cite{Tataria2021,Alsabah2021,Jiang2021}:
	\begin{itemize}
		\item \emph{Throughput}: The network would be able to provide a peak data rate of 1 Tbps and an average data rate of 100 Gbps per user.
		\item \emph{Latency}: Sub-millisecond end-to-end latency would be achieved for low-latency applications like autonomous driving and remote surgery.
		\item \emph{Reliability}: A success rate of 99.9999\% would be guaranteed for ultra-reliable applications like industrial automation and cooperative robotics.
		\item \emph{Connectivity}: The number of connected devices per kilometer square would be increased to 10 million for supporting \gls{ioe}.
		\item \emph{Mobility}: Commercial airlines with a maximal velocity of 1000 km/h would be the target application scenario.
		\item \emph{Energy efficiency}: Power consumption has been a major criticism for 5G. It is expected that energy per bit would be reduced by over 90\% in 6G to reduce carbon footprints.
		\item \emph{Positioning accuracy}: Thanks to THz base stations, a 3D positioning accuracy of centimeter level may be achieved for indoor and outdoor environments.
		\item \emph{Coverage}: Poor coverage has been another bottleneck for 5G. A terrestrial-satellite-aerial integrated network would provide a ubiquitous and uniform coverage for urban, rural, and remote areas.
		\item \emph{Security and privacy}: Physical-layer security can be improved with narrower beams at higher frequencies and destructive scattering at the environment. Privacy can be enhanced with federated learning and homomorphic encryption.
		% \item \emph{Superintelligent}: The network may integrate human, machine, environment, and \gls{ai} into a superintelligent system that can sense, communicate, and act in a coordinated manner.
	\end{itemize}

@@

	\begin{subsection}{Concept}
		\gls{ris} is commonly known as a planar surface involving numerous wave scattering elements (a.k.a. unit cells, reflective patches), whose amplitude and phase responses can be engineered in real-time to achieve a desired radiation pattern.
		As shown in Fig. \ref{fg:ris_architecture}, its typical architecture consists of three stacked layers and a controller \cite{Wu2020}.
		The top layer is a two-dimensional array of scattering elements printed on a dielectric substrate.
		The elements directly interact with the impinging waves, which are usually fabricated from metamaterial or patch/dipole antennas with sub-wavelength dimension and spacing.
		The middle layer is a copper ground plate that provides voltage reference and avoids signal leakage.
		The bottom later is a circuit board that associate each element with adjustable components, such as varactor and \gls{pin} diodes \cite{Dai2020}.
		It also hosts a \gls{fpga} controller that controls the circuit and coordinate with transceivers in the network.
		By adjusting the scatter response of all elements, the \gls{ris} can effectively manipulate the wavefront for a constructive or destructive superposition and thus improve the ambient wireless environment.
		\begin{figure}
			\centering
			\includegraphics[width=0.9\textwidth]{ris_architecture.pdf}
			\caption{A typical architecture of \gls{ris}. Modified from \cite{Wu2020}.}
			\label{fg:ris_architecture}
		\end{figure}
	\end{subsection}

@@

		\item Chapter \ref{ch:introduction} provides an overview of the thesis. It introduces the background and motivation, discusses the characteristics and applications of \gls{ris}, and summarizes the objectives and contributions of each research chapter. A list of publications is also provided.

>>>>

\begin{section}{Motivation}
	The quest for better wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
	Great successes have been made at the transmitter and receiver sides over the past century, and the communications society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
	By 2025, global mobile data traffic is expected to reach {607} exabytes per year \cite{Tariq2020} while the number of connected devices may exceed {75} billion \cite{Georgiev2024}.
	At the same time, wireless applications are also evolving in various forms to address world-changing incidents like COVID-19, climate change, geopolitical tensions, and \gls{ai} revolution.
	An initial attempt was made in 5G where the network prioritizes among high-throughput, ubiquitous-coverage, high-reliability, low-latency, massive-connectivity, and energy-efficient services \cite{Shafi2017}.
	However, the desire of human and machine for better communication shows no signs of slowing down.
	Emerging applications such as smart cities, autonomous driving, telemedicine, extended reality, federated learning, and generative intelligence are calling for a stronger and smarter wireless infrastructure.
	It is envisioned that 6G will be designed to meet the following requirements \cite{Tataria2021,Alsabah2021,Jiang2021}:
	\begin{itemize}
		\item \emph{Throughput}: The network would be able to provide a peak data rate of 1 Tbps and an average data rate of 100 Gbps per user.
		\item \emph{Latency}: Sub-millisecond end-to-end latency would be achieved for low-latency applications like autonomous driving and remote surgery.
		\item \emph{Reliability}: A success rate of 99.9999\% would be guaranteed for ultra-reliable applications like industrial automation and cooperative robotics.
		\item \emph{Connectivity}: The number of connected devices per kilometer square would be increased to 10 million for supporting \gls{ioe}.
		\item \emph{Mobility}: Commercial airlines with a maximal velocity of 1000 km/h would be the target application scenario.
		\item \emph{Energy efficiency}: Power consumption has been a major criticism for 5G. It is expected that energy per bit would be reduced by over 90\% in 6G to reduce carbon footprints.
		\item \emph{Positioning accuracy}: Thanks to THz base stations, a 3D positioning accuracy of centimeter level may be achieved for indoor and outdoor environments.
		\item \emph{Coverage}: Poor coverage has been another bottleneck for 5G. A terrestrial-satellite-aerial integrated network would provide a ubiquitous and uniform coverage for urban, rural, and remote areas.
		\item \emph{Security and privacy}: Physical-layer security can be improved with narrower beams at higher frequencies and destructive scattering at the environment. Privacy can be enhanced with federated learning and homomorphic encryption.
		% \item \emph{Superintelligent}: The network may integrate human, machine, environment, and \gls{ai} into a superintelligent system that can sense, communicate, and act in a coordinated manner.
	\end{itemize}

@@

	\begin{subsection}{Concept}
		\gls{ris} is commonly known as a planar surface involving numerous wave scattering elements (a.k.a. unit cells, reflective patches), whose amplitude and phase responses can be engineered in real-time to achieve a desired radiation pattern.
		It behaves like a delicate \gls{rf} mirror with adjustable curvature and orientation, which allows the incident signals to be focused and redirected in a particular direction.
		As shown in Fig. \ref{fg:ris_architecture}, its typical architecture consists of three stacked layers and a controller \cite{Wu2020}.
		The top layer is a two-dimensional array of scattering elements printed on a dielectric substrate.
		The elements directly interact with the impinging waves, which are usually fabricated from metamaterial or patch/dipole antennas with sub-wavelength dimension and spacing.
		The middle layer is a copper ground plate that provides voltage reference and avoids signal leakage.
		The bottom later is a circuit board that associate each element with adjustable components, such as varactor and \gls{pin} diodes \cite{Dai2020}.
		It also hosts a \gls{fpga} controller that controls the circuit and coordinate with transceivers in the network.
		By adjusting the scatter response of all elements, the \gls{ris} can effectively manipulate the wavefront for a constructive or destructive superposition and thus improve the ambient wireless environment.
		\begin{figure}
			\centering
			\includegraphics[width=0.9\textwidth]{ris_architecture.pdf}
			\caption{A typical architecture of \gls{ris}. Modified from \cite{Wu2020}.}
			\label{fg:ris_architecture}
		\end{figure}
	\end{subsection}

@@

		\item Chapter \ref{ch:introduction} provides an overview of the thesis. It introduces the motivation and objectives, discusses the characteristics and applications of \gls{ris}, and summarizes the topics and contributions of each research chapter. A list of publications is also provided.

### 2024-03-16 content/chapter_2.tex
:pencil: Update motivation and add concept
:lipstick: Add reflected wave plots

\begin{section}{\glsfmtfull{ris}}
	% \begin{subsection}{Programmable Metamaterials}

	% \end{subsection}

	\begin{subsection}{Hardware Implementation}
		\begin{subsubsection}{Programmable Metamaterials}
			Metamaterials refer to artificial structures engineered for unusual properties that may not be found in nature.
			The concept was initially proposed by Victor Veselago in 1967, who conjectured the existence of mediums with negative dielectric constant $\epsilon < 0$ and negative permeability $\mu < 0$ \cite{Veselago1968}.
			Such metamaterials are known as ``negative-index'' because the refraction index is defined as the \emph{negative} square root $n = - \sqrt{\epsilon \mu} < 0$, in order to be consistent with Maxwell's equations.
			It was not until 1999 that their feasibility was experimentally demonstrated by John Pendry at Imperial College using split-ring resonators \cite{Pendry1999}.
			Since then, metamaterials have attracted significant interests due to their counterintuitive properties, to name a few:
			\begin{itemize}
				\item \emph{Negative refraction:} As shown in Fig. \ref{fg:nim_refraction}, the incident and refracted rays stay at the same side of the normal axis. This phenomenon is in contrast to the usual refraction but can still be predicted from Snell's law
				\begin{equation}
					\frac{\sin \theta_1}{\sin \theta_2} = n.
				\end{equation}
				\begin{figure}[H]
					\centering
					\resizebox{0.5\columnwidth}{!}{
						\input{assets/chapter_2/nim_refraction.tex}
					}
					\caption{Refraction of electromagnetic waves at the interface between a positive-index and a negative-index material.}
					\label{fg:nim_refraction}
				\end{figure}
				\item \emph{Opposite wave direction:} As shown in Fig. \ref{fg:nim_flows}, the wave vector and energy flow (indicated by the Poynting vector) are opposite to each other in a negative-index material. This can be inferred from the electric field equation
				\begin{equation}
					\vec{E} = \vec{E}_0 \exp(\jmath k z - \jmath \omega t)
				\end{equation}
				where $k = k_0 n < 0$ is the wavenumber, $\vec{E}_0$ and $k_0$ are the free-space reference, $z$ is the propagation distance, $\omega$ is the angular frequency, and $t$ is the time.
				Negative-index materials are thus also called ``left-hand'' because the propagation direction of the electric and magnetic fields can be determined by a left-hand rule.
				\begin{figure}[H]
					\centering
					\resizebox{0.5\columnwidth}{!}{
						\input{assets/chapter_2/nim_flows.tex}
					}
					\caption{Wave and energy flows in a negative-index material.}
					\label{fg:nim_flows}
				\end{figure}
			\end{itemize}
		\end{subsubsection}

		\begin{subsubsection}{Physical Architecture}

@@

	\begin{subsection}{Comparison with Reflectarrays and Relays}
		\begin{subsubsection}{Functionality}

		\begin{subsubsection}{Reconfigurability}

		\begin{subsubsection}{Complexity}

		\begin{subsubsection}{Power Consumption}

		\begin{subsubsection}{Dimension and Cost}

		\begin{subsubsection}{Applications}

>>>>

\begin{section}{\glsfmtfull{ris}}
	\begin{subsection}{Programmable Metamaterials}
		Metamaterials refer to artificial structures engineered for unusual properties that may not be found in nature.
		The concept was initially proposed by Victor Veselago in 1967, who conjectured the existence of mediums with negative dielectric constant $\epsilon < 0$ and negative permeability $\mu < 0$ \cite{Veselago1968}.
		Such metamaterials are known as ``negative-index'' because the refraction index is defined as the \emph{negative} square root $n = - \sqrt{\epsilon \mu} < 0$, in order to be consistent with Maxwell's equations.
		It was not until 1999 that their feasibility was experimentally demonstrated by John Pendry at Imperial College using split-ring resonators \cite{Pendry1999}.
		Since then, metamaterials have attracted significant interests due to their counterintuitive properties, to name a few:
		\begin{itemize}
			\item \emph{Negative refraction:} As shown in Fig. \ref{fg:nim_refraction}, the incident and refracted rays stay at the same side of the normal axis. This phenomenon is in contrast to the usual refraction but can still be predicted from Snell's law
			\begin{equation}
				\frac{\sin \theta_1}{\sin \theta_2} = n.
			\end{equation}
			\begin{figure}[H]
				\centering
				\subfloat[Negative Index Material\label{fg:nim_refraction}]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/chapter_2/nim_refraction.tex}
					}
				}
				\subfloat[Positive Index Material\label{fg:pim_refraction}]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/chapter_2/pim_refraction.tex}
					}
				}
				\caption{Refraction in negative and positive index materials. Incident and refracted rays stay at the same side of the normal axis in a negative-index material.}
			\end{figure}
			\item \emph{Opposite wave direction:} As shown in Fig. \ref{fg:nim_flows}, the wave vector and energy flow (indicated by the Poynting vector) are opposite to each other in a negative-index material. This can be inferred from the electric field equation
			\begin{equation}
				\vec{E} = \vec{E}_0 \exp(\jmath k z - \jmath \omega t)
			\end{equation}
			where $k = k_0 n < 0$ is the wavenumber, $\vec{E}_0$ and $k_0$ are the free-space electric field and wavenumber reference, $z$ is the propagation distance, $\omega$ is the angular frequency, and $t$ is the time.
			Negative-index materials are thus also called ``left-hand'' because the propagation direction of the electric and magnetic fields can be determined by a left-hand rule.
			\begin{figure}[H]
				\centering
				\resizebox{0.5\columnwidth}{!}{
					\input{assets/chapter_2/nim_flows.tex}
				}
				\caption{Wave and energy have opposite directions in a negative-index material.}
				\label{fg:nim_flows}
			\end{figure}

		\end{itemize}

		% TODO Programmable
		\begin{figure}[H]
			\centering
			\subfloat[Incident Wave\label{fg:wave_incident}]{
				\resizebox{!}{4.04cm}{
					\input{assets/chapter_2/wave_incident.tex}
				}
			}
			\subfloat[Reflected Wave\label{fg:wave_reflected}]{
				\resizebox{!}{4cm}{
					\input{assets/chapter_2/wave_reflected.tex}
				}
			}
			\caption{Incident and reflected waves in a programmable metamaterial.}
		\end{figure}
	\end{subsection}

@@

\end{section}
